\Title

### 2021-01-26 manuscript/manuscript.tex
Use percentages in the manuscript as well

The results show that the interpolation RMS error for gradient-boosting is
generally larger than the error for regular equivalent sources.
The error decreases asymptotically to within $\sim 40\%$ of the regular
equivalent sources for windows with an area greater than $\sim 35\%$ of the
survey area.
The computation time similarly decreases with window size, with the
gradient-boosting being generally faster than the regular equivalent sources
for windows with an area greater than $\sim 20\%$ of the survey area.
As the window size increases, both RMS error and computation time appear to
stabilize to nearly constant levels.

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Comparison of the interpolation RMS error and computation time for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Both methods used the same source positions (block-averaged sources
        with a relative depth).
        Window sizes are given as a fraction of the survey area (e.g., 1
        represents a window with the same area as the survey) and window
        overlap is given as a fraction of the window size (e.g., 0.5 equals
        50\% overlap).
        Computation time refers to the time required to estimate the source
        coefficients and is reported as a ratio between the gradient-boosted
        and the regular equivalent sources.
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars represent 1 standard deviation) of results using
        different seeds for the pseudo-random number generator.
        (a)~RMS error between the target grid and interpolation results and
        (b)~computation time as a function of window size.
        (c)~RMS error between the target grid and interpolation results and
        (d)~computation time as a function of window overlap.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}

>>>>

The results show that the interpolation RMS error for gradient-boosting is
generally larger than the error for regular equivalent sources.
The error decreases asymptotically to within $\sim 40\%$ of the regular
equivalent sources for windows with an area greater than $\sim 10\%$ of the
survey area.
The computation time similarly decreases with window size, with the
gradient-boosting being generally faster than the regular equivalent sources
for windows with an area greater than $\sim 5\%$ of the survey area.
As the window size increases, both RMS error and computation time appear to
stabilize to nearly constant levels.

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Comparison of the interpolation RMS error and computation time for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Both methods used the same source positions (block-averaged sources
        with a relative depth).
        Window sizes are given as a percentage of the survey area (e.g., 100
        represents a window with the same area as the survey) and window
        overlap is given as a percentage of the window size.
        Computation time refers to the time required to estimate the source
        coefficients and is reported as a ratio between the gradient-boosted
        and the regular equivalent sources.
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars represent 1 standard deviation) of results using
        different seeds for the pseudo-random number generator.
        (a)~RMS error between the target grid and interpolation results and
        (b)~computation time as a function of window size.
        (c)~RMS error between the target grid and interpolation results and
        (d)~computation time as a function of window overlap.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}
